SDR enhancement by clouds

### 2024-03-08 article/article.Rmd
Commit 2024-03-08 14:14

output: 
 #  rticles::mdpi_article:
 #    extra_dependencies:  longtable
 #    keep_tex:            yes
  bookdown::pdf_document2:
    number_sections:  no
    fig_caption:      yes
    keep_tex:         no
    latex_engine:     xelatex
    toc:              no
    toc_depth:        4
    fig_width:        7
    fig_height:       4.5
    documentclass:    article
    classoption:      a4paper,oneside
    fontsize:         12pt
    geometry:         "left=0.75in,right=0.75in,top=0.75in,bottom=0.75in"
    link-citations:   yes
    colorlinks:       yes
    urlcolor:         blue
    biblio-style:     apalike
    bookdown::word_document2: default
---

@@

@@

>>>>

output: 
 #  rticles::mdpi_article:
 #    extra_dependencies:  longtable
 #    keep_tex:            yes
  bookdown::pdf_document2:
    number_sections:  yes
    fig_caption:      yes
    keep_tex:         no
    latex_engine:     xelatex
    toc:              yes
    toc_depth:        4
    fig_width:        7
    fig_height:       4.5
    documentclass:    article
    classoption:      a4paper,oneside
    fontsize:         12pt
    geometry:         "left=0.75in,right=0.75in,top=0.75in,bottom=0.75in"
    link-citations:   yes
    colorlinks:       yes
    urlcolor:         blue
    biblio-style:     apalike
    bookdown::word_document2: default
---

@@

<!-- todo stop long tails on hist -->
<!-- hist retative frequency label -->

<!-- Whisky plot relative between months -->
<!-- weight (Nmonth / Nmaxmonth) -->

<!-- whisky plots relative to GLB -->

<!-- set of yearly plots -->

@@

# Appendix {.unnumbered}
